Gafo-cc visuals

### 2022-06-21 analysis/gafo-cc-analysis.Rmd
prep model run on cluster

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         children = scale(children),
         household = scale(household),
         youngerchildren = scale(youngerchildren),
         touchscreen = factor(touchscreen),
        screen = factor(screen))

unique(mdata$community)
```

```{r}
bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (1|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

@@

```{r}
bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx  + (1|subjid) + (screen + children + household|community), 
                              data   = mdata%>%filter(community != "chimfunshi_kumwenda"), 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

>>>>

```{r}
mdata <- read_csv("../data/gafo-cc-clean-data.csv")%>%
  mutate(ageinyears = scale(ageinyears),
         targetcentralityx = scale(targetcentralityx),
         trialnr = scale(trialnr),
         children = scale(children),
         household = scale(household),
         younger_children = scale(younger_children),
         touchscreen = factor(touchscreen),
        screen = factor(screen))%>%
  filter(community == "leipzig" |community == "akure")

mdata%>%
  ggplot(aes(x = abs(clickdistfromtargetcenterx)))+
  geom_density()

c(
  lower = exp(4 - 2 * 1.75),
  higher = exp(4 + 2 * 1.75)
)

```{r}
bm_gam <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_log <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
                              data   = mdata, 
                              family = lognormal(),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_slog <- brm(abs(clickdistfromtargetcenterx) ~ 1, 
                              data   = mdata, 
                              family = shifted_lognormal(),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_exg<- brm(abs(clickdistfromtargetcenterx) ~ 1, 
                              data   = mdata, 
                              family = exgaussian(),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_wei<- brm(abs(clickdistfromtargetcenterx) ~ 1, 
                              data   = mdata, 
                              family = weibull(),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

loo_compare(bm_gam, bm_log,bm_slog, bm_exg,bm_wei)%>%as_tibble(rownames = "model")

pp_check(bm_gam)+xlim(0,3000)
pp_check(bm_log)+xlim(0,3000)
pp_check(bm_slog)+xlim(0,3000)
pp_check(bm_exg)+xlim(0,3000)
pp_check(bm_wei)+xlim(0,3000)
```

```{r}
bm_base_gam <- brm(abs(clickdistfromtargetcenterx) ~ targetcentralityx + (trialnr|subjid) + (0+ageinyears|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 2000, 
                              iter   = 5000,
                   control = list(adapt_delta = 0.95),
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

bm_base_wei <- brm(abs(clickdistfromtargetcenterx) ~ targetcentralityx + (trialnr|subjid) + (0+ageinyears|community), 
                              data   = mdata, 
                              family = weibull(),
                              warmup = 2000, 
                              iter   = 5000, 
                   control = list(adapt_delta = 0.95),
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

loo_compare(bm_base_gam,bm_base_wei)%>%as_tibble(rownames = "model")

pp_check(bm_base_gam)+xlim(0,3000)
pp_check(bm_base_wei)+xlim(0,3000)

```{r}
bm_base <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx + (trialnr|subjid) + (ageinyears|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

@@

```{r}
bm_screen <- brm(abs(clickdistfromtargetcenterx) ~ ageinyears  + targetcentralityx  + (1|subjid) + (screen + children + household|community), 
                              data   = mdata, 
                              family = Gamma(link = "log"),
                              warmup = 1000, 
                              iter   = 4000, 
                              chains = 4, 
                              cores  = 4)%>%
  add_criterion(., c("waic","loo"))

### 2022-06-21 analysis/gafo-cc-data-processing.Rmd
prep model run on cluster

@@

data <- bind_rows(
  data_namibia,
  data_leipzig,
  data_nigeria,
  data_zambia
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

>>>>

```{r}
tidy_data_zambia%>%
  summarise(n = n_distinct(subjID))
```

@@

data <- bind_rows(
  data_namibia%>%rename(younger_children = youngerchildren),
  data_leipzig,
  data_nigeria,
  data_zambia
)%>%
  #mutate(community = paste0("c",as.character(as.numeric(as.factor(community)))))%>%
  filter(trialtype == "test")

@@

data_nigeria$younger_children
```

### 2022-06-21 analysis/gafo-cc-visuals.Rmd
prep model run on cluster

```{r}
data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))
```

@@

```{r}
data%>%
  group_by(targetcentralityx)%>%
  #summarise(impr = mean(clickdistfromtargetcenterx))%>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2))%>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx))+
  geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
  #geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
  #geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
  geom_point(pch = 1, alpha = 0.75)+
  #ylim(-1500,1500)+
  theme_minimal()

@@

>>>>

```{r}
data%>%
  group_by(community)%>%
  summarise(n= n_distinct(subjid))

data%>%
  summarise(n= n_distinct(subjid))
```

@@

```{r}
random <- tibble()

for (j in 1:100) {

for (i in 1:960) {

  chance = abs(i + sample(-960:960,1))

  random <- bind_rows(
    random,
    tibble(location = i, 
           iter = j,
           lower = chance, 
           upper = -chance)
  )
}

}

chance <- random%>%
  group_by(location)%>%
  summarise(lower = mean(lower),
            upper = mean(upper))

data%>%
  group_by(targetcentralityx)%>%
  mutate(chance_upper = (targetcentralityx + 960)/2,
         chance_lower = -((targetcentralityx + 960)/2),
         center_lower = -targetcentralityx,
         center_upper = targetcentralityx)%>%
  ggplot(aes(x = targetcentralityx, y = clickdistfromtargetcenterx, col = community))+
  geom_hline(yintercept = 0, lty = 3, alpha = 0.75)+
  geom_line(aes(x = targetcentralityx, y = center_upper), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = center_lower), lty = 1, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_upper), lty = 3, alpha = .75, col = "firebrick")+
  geom_line(aes(x = targetcentralityx, y = chance_lower), lty = 3, alpha = .75, col = "firebrick")+
  geom_point(pch = 1, alpha = 0.5)+
  scale_color_colorblind()+
  #ylim(-1500,1500)+
  theme_minimal()

range(data$targetcentralityx)
```

@@

```{r}
pscreen1 <- data%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(community, subjid, predictor, value)%>%
  summarise(mean= mean(abs(clickdistfromtargetcenterx)))

pscreen2 <- data%>%
  mutate(screen = factor(screen),
         touchscreen = factor(touchscreen))%>%
  pivot_longer(cols = c(screen, touchscreen), names_to = "predictor", values_to = "value")%>%
  group_by(community, predictor, value)%>%
  tidyboot_mean(col= abs(clickdistfromtargetcenterx))

ggplot(pscreen%>%filter(!is.na(value)), aes(x = value, y = mean, col = community))+
  geom_point(data = pscreen1%>%filter(!is.na(value)), aes(x = value, y = mean, col = community), pch = 1, alpha = .5, position = position_dodge(width = .5))+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.75, position = position_dodge(width = .5))+
  facet_grid(~predictor, scales = "free_x")+
  scale_x_discrete(labels = c("no", "yes"))+
  scale_color_colorblind()+
  #ylim(0,1000)+
  theme_few()
```

```{r}
pred <- data%>%
  group_by(community, subjid, household, children, younger_children)%>%
  summarise(mean= mean(abs(clickdistfromtargetcenterx)))%>%
  pivot_longer(cols = c(household, children, younger_children), names_to = "predictor", values_to = "value")%>%
  group_by(community,predictor)%>%
  mutate(value = scale(value))

ggplot(pred, aes(x = value, y = mean, col = community))+
  geom_point(pch = 1)+
  geom_smooth(method = "glm")+
  facet_grid(~predictor, scales = "free_x")+
  stat_cor()+
  scale_color_colorblind()+
  ylim(0,1000)+
  theme_minimal()
```
